Title Goes Here

### 2020-02-24 paper/paper.tex
Expanded on tail rec step in flowchart
Attempt at tail recursion equations

\begin{tikzpicture}[node distance=2cm]
\node (start) [startstop] {Core from GHC};
  \node (tailrec) [process, below of=start]{Transform tail recursion (if applicable)};
  \node (findmark) [process, below of=tailrec]{Find marked expression and erase mark};
    \node (handlecase) [process, below of=findmark]{Mark scrutinee};
    \node (handleprim) [process, right of=handlecase, xshift=1.6cm]{Encode as EDSL primitive};
    \node (handleapp) [process, right of=handleprim, xshift=1.6cm]{Wrap with \ttt{Construct} and \ttt{ConstructAp}};

@@

\begin{align*}
  &C\expr{\ttt{externalize (x + y)}} = \ttt{Add $M\expr{\ttt{x}}$ $M\expr{\ttt{y}}$}\\
  &C\expr{\ttt{externalize (case scrutinee of \{ ... \})}} = \ttt{CaseExp $M\expr{\ttt{scrutinee}}$ } B\expr{\ttt{\{ ... \}}}\\
  &\\
  &B\expr{\ttt{\{ K x0 ... xN $\rarr$ body0; ... \}}} = \ttt{SumMatchExp }P\expr{\ttt{x0 ... xN $\rarr$ body0}}\; B\expr{\ttt{\{ ... \}}}\\
  &B\expr{\ttt{\{ K x0 ... xN $\rarr$ body \}}} = \ttt{OneSumMatchExp }P\expr{\ttt{x0 ... xN $\rarr$ body}}\\
  &B\expr{\ttt{\{ \}}} = \ttt{EmptyMatch}\\
  &\\
  &P\expr{\ttt{x0 x1 ... $\rarr$ body}} = \ttt{ProdMatchExp }A\expr{\ttt{$\lambda$ x0 $\rarr$ $P\expr{\ttt{x1 ... $\rarr$ body}}$}}\\
  &P\expr{\ttt{x $\rarr$ body}} = \ttt{OneProdMatchExp }A\expr{\ttt{$\lambda$ x $\rarr$ body}}\\
  &P\expr{\ttt{ $\rarr$ body}} = \ttt{NullaryMatch $M\expr{\ttt{body}}$}\\
  &\\
  &A\expr{\ttt{$\lambda$(x :: a) $\rarr$ body}} = \ttt{Lam (Name @a uniq) $M\expr{\ttt{body$[\ttt{x} \mapsto \ttt{Var uniq}]$}}$}\text{\;\;\;\;\;(where \ttt{uniq} is a globally unique identifier)}\\
  &\\
  &M\expr{\ttt{(x :: a)}} =
    \begin{cases}
      \ttt{externalize x} & \text{if}\; \nexists t, a\; \typeeq E\; t\\
      \ttt{x} & \text{if}\; \exists t, a\; \typeeq E\; t
    \end{cases}
\end{align*}

>>>>

\begin{tikzpicture}[node distance=2cm]
\node (start) [startstop] {Core from GHC};
  \node (tailrec) [process, below of=start]{Transform tail recursion of definitions with a mark (when applicable)};
  \node (findmark) [process, below of=tailrec]{Find marked expression and erase mark};
    \node (handlecase) [process, below of=findmark]{Mark scrutinee};
    \node (handleprim) [process, right of=handlecase, xshift=1.6cm]{Encode as EDSL primitive};
    \node (handleapp) [process, right of=handleprim, xshift=1.6cm]{Wrap with \ttt{Construct} and \ttt{ConstructAp}};

@@

\begin{align*}
  D&\expr{\ttt{f x = internalize (externalize (case s of \{ ... \}))}}\\
      &:= \begin{cases}
        \ttt{f = internalize $C^{*}\expr{\ttt{externalize (runIter $A\expr{\lambda \ttt{x} \rarr \ttt{case s of $T_{\ttt{f}}\expr{\ttt{\{ ... \}}}$}}$)}}$} & \text{if \ttt{f} occurs in \ttt{\{ ... \}}}\\
        \ttt{f x = internalize $C^{*}\expr{\ttt{externalize (case s of \{ ... \})}}$} & \text{otherwise}
      \end{cases}\\
\end{align*}

\begin{align*}
  T_{\ttt{f}}&\expr{\ttt{\{ K x0 ... xN $\rarr$ body0; ... \}}} := \\
    &:=
      \begin{cases}
        \ttt{\{ K x0 ... xN} \rarr \ttt{body}[\ttt{f} \mapsto \ttt{Step}]; T_{\ttt{f}}\expr{\ttt{\{ ... \}}}\ttt{ \}} & \text{if \ttt{f} occurs in \ttt{body}}\\
        \ttt{\{ K x0 ... xN $\rarr$ Done body; ... \}} & \text{otherwise}
      \end{cases}\\
  T_f&\expr{\ttt{\{ \}}} := \ttt{\{ \}}\\
\end{align*}
\begin{align*}
  &C^{*}\expr{\ttt{x}} :=
    \begin{cases}
      x & \text{if x has no marked subexpressions}\\
      C^{*}\expr{C\expr{\ttt{externalize y}}} & \text{if \ttt{externalize y} is the first marked subexpression of \ttt{x}}\\
    \end{cases}\\
\end{align*}
\begin{align*}
  &C\expr{\ttt{externalize (runIter x)}} := \ttt{TailRec $M\expr{\ttt{x}}$}\\
  &C\expr{\ttt{externalize (x + y)}} := \ttt{Add $M\expr{\ttt{x}}$ $M\expr{\ttt{y}}$}\\
  &C\expr{\ttt{externalize (case scrutinee of \{ ... \})}} := \ttt{CaseExp $M\expr{\ttt{scrutinee}}$ } B\expr{\ttt{\{ ... \}}}\\
  &\\
  &B\expr{\ttt{\{ K x0 ... xN $\rarr$ body0; ... \}}} := \ttt{SumMatchExp }P\expr{\ttt{x0 ... xN $\rarr$ body0}}\; B\expr{\ttt{\{ ... \}}}\\
  &B\expr{\ttt{\{ K x0 ... xN $\rarr$ body \}}} := \ttt{OneSumMatchExp }P\expr{\ttt{x0 ... xN $\rarr$ body}}\\
  &B\expr{\ttt{\{ \}}} = \ttt{EmptyMatch}\\
  &\\
  &P\expr{\ttt{x0 x1 ... $\rarr$ body}} := \ttt{ProdMatchExp }A\expr{\ttt{$\lambda$ x0 $\rarr$ $P\expr{\ttt{x1 ... $\rarr$ body}}$}}\\
  &P\expr{\ttt{x $\rarr$ body}} := \ttt{OneProdMatchExp }A\expr{\ttt{$\lambda$ x $\rarr$ body}}\\
  &P\expr{\ttt{ $\rarr$ body}} := \ttt{NullaryMatch $M\expr{\ttt{body}}$}\\
  &\\
  &A\expr{\ttt{$\lambda$(x :: a) $\rarr$ body}} := \ttt{Lam (Name @a uniq) $M\expr{\ttt{body$[\ttt{x} \mapsto \ttt{Var uniq}]$}}$}\text{\;\;\;\;\;(where \ttt{uniq} is a globally unique identifier)}\\
  &\\
  &M\expr{\ttt{(x :: a)}} :=
    \begin{cases}
      \ttt{externalize x} & \text{if}\; \nexists t, a\; \typeeq E\; t\\
      \ttt{x} & \text{if}\; \exists t, a\; \typeeq E\; t
    \end{cases}
\end{align*}
